Proposed Solution

### 2017-01-24 CAV17/secs/motiv.tex
fix output for rule

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
  FINE GRAINED ERROR:
  Expected "max_connections" * "sort_buffer_size"
               > "key_buffer_size"
\end{lstlisting}

>>>>

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
[FINE GRAINED ERROR: Expected "max-connections[mysqld]" * "sort-buffer-size[mysqld]"
  {gt = 63, lt = 5, eq = 0} "key-buffer-size[mysqld]"
\end{lstlisting}
